---
title: "K-Mean Clustering"
author: "Shekhar Lamichhane Magar"
output:
  pdf_document: default
  html_notebook: default
---

# Problem and Targeted Solution

* Apply K-means clustering approach to identify customer groups

Task 1: Install and import necessary packages

```{r}
# Set CRAN mirror
options(repos = c(CRAN = "https://cloud.r-project.org/"))

# Install required packages
if (!require(ggplot2)) {
  install.packages("ggplot2")
}
if (!require(factoextra)) {
  install.packages("factoextra")
}

# Load the packages
library(ggplot2)
library(factoextra)

```
* Load packages and use them

```{r}
library(ggplot2)
library(factoextra)
```
Task 2: Set random seed

```{r}
# Set random seed
set.seed(7696)
```
Task 3: Load Data

* Create a folder for today's lab and copy the data file(.csv file) into the folder.
* Setup the folder you created as Rstudio's working directory as we discussed during previous lab sessions.

```{r}
# Load data
data <- read.csv("Mall_Customers.csv")
```

Task 4:  K-means clustering using 2 attributes; “Annual_Income” and “Spending_Score”

Let’s cluster customers into 5 groups using the attributes “Annual_Income” and“Spending_Score”.
a) Filter targeted attributes
Create a new data frame, which only contains the columns “Annual_Income” and“Spending_Score”

```{r}
# filter data by column name
filtered_data1 <- data[, c("Annual_Income","Spending_Score")]
```

b) Visualise data
See how the data points are located in the space using a scatter plot to get anunderstanding about
the data you are going to cluster

```{r}
# Draw a scatter plot
ggplot(data, aes(x = Annual_Income, y = Spending_Score) ) + geom_point()
```

c) Apply K-means clustering
Initially we need to define a value for K (number of clusters).Since
out target is to find 5 customer groups, K = 5.

```{r}
# Find 5 clusters using K-means clustering
clusters <- kmeans(filtered_data1, 5)
# View cluster details
clusters
```

Q1: What can you tell about the customer groups you obtained?

d) Visualise clusters

```{r}
# Extract cluster indices
cluster_index <- as.factor(clusters$cluster)
# View cluster details
ggplot(filtered_data1, aes(x = Annual_Income, y = Spending_Score, color =
cluster_index)) + geom_point()

```

Task 5: K-means clustering using more attributes; “Age”, “Annual_Income” and
“Spending_Score”.
 
a) Filter targeted attributes
Create a new data frame which only contains the
columns “Age”, “Annual_Income” and“Spending_Score”.

```{r}
# filter data by column name
filtered_data2 <- data[, c("Age", "Annual_Income","Spending_Score")]
```

b) Apply K-means clustering
Similarly, as before, we can apply clustering to new data frame (filtered_data2).

```{r}
# Find 5 clusters using K-means clustering
clusters2 <- kmeans(filtered_data2, 5)
# View cluster details
clusters2
```

Q2: What can you tell about the customer groups by considering all 3 attributes?
c) Visualise clusters
Now, our clusters are in 3-dimensional spacewith the dimensions “Age”,“Annual_Income”and
“Spending_Score”. Thus, we cannot simply use the above graph generation method.
There are methods which helps us to map multidimensional spaces with more than 2dimensions into 2 
dimensional spaces for visualisation purpose.

```{r}
# Visualise clusters in 3 or high dimensional spaces
fviz_cluster(clusters2, data = filtered_data2, geom = c("point"))
```

6) Overcome initial centroid problem
As we discussed, having multiple runs is the simplest way which help
overcoming initial centroid problem.
Just adding 1 argument (nstart) to the function, you can have multiple runs.

```{r}
# Find 5 clusters using K-means clustering
clusters3 <- kmeans(filtered_data2, 5, nstart = 25)
# View cluster details
clusters3
# Visualise clusters in 3 or high dimensional spaces
fviz_cluster(clusters3, data = filtered_data2, geom = c("point"))
```

* Note:
a) nstart = 25 means, you are having 25 random initialisations. Final / resulting 
clusteringwould be the best one.

b) You want see clear difference in your new clusters compared to previous clusters, if the 
bestclustering is randomly selected already.