---
title: "Data Enrichment_Lab10(Part2)"
author: "Shekhar Lamichhane Magar"
output:
  pdf_document: default
  html_notebook: default
---

## Deduplication
Task: Load the data
```{r}
library("tidyverse")
```

Task: Creating a vector
```{r}
x <- c(1,2,4,5,4,6)
```

Task: checking a duplicated value
```{r}
duplicated(x)
```

Task: Not Get duplicated value from the vector
```{r}
x[!duplicated(x)]
``` 

Task: Filtering non duplicated value of iris dataset on sepal.width column
```{r}
iris[!duplicated(iris$Sepal.Width), ]
```

### Remove duplicate rows in a data frame
Task: checking distinct values
```{r}
iris %>% distinct()
```

Task: removing duplicated rows on sepal.length
```{r}
# Remove duplicated rows based on Sepal.Length
iris %>% distinct(Sepal.Length, .keep_all = TRUE)
```

```{r}
# Remove duplicated rows based on Sepal.Length and Petal.Width
iris %>% distinct(Sepal.Length, Petal.Width, .keep_all = TRUE)

```

### Summary
In this section, we describe key functions for identifying and removing duplicate data:
• Remove duplicate rows based on one or more column values: my_data %>% distinct(Sepal.Length)
• R base function to extract unique elements from vectors and data frames: unique(my_data)
• R base function to determine duplicate elements: duplicated(my_data)


## 2) Grouping

Task: creating the variable by storing group of species of iris dataset
```{r}
# First, we have to define which column we are going to use to group. 
# In this case we use the species of the plant.
my_group <- group_by(iris, Species)

# Now using "summarize_all", we define which function we use to group the values. for an example we can use mean.
summarize_all(my_group, funs(mean))
```

Task: Load the survey data
```{r}
# Load survey data set
surveys <- read.csv("survey.csv")
```

Task: grouping surveys by sex and adding mean_weight column to get mean and also removing null values
```{r}
surveys %>%
  group_by(sex) %>% 
  summarize(mean_weight = mean(wgt, na.rm = TRUE))

```

Task: grouping by sex and species
```{r}
surveys %>%
group_by(sex, species) %>%
summarize(mean_weight = mean(wgt, na.rm = TRUE))
```

Task: grouping by sex and species and creating mean_weight to store mean
```{r}
surveys %>%
  group_by(sex, species) %>%
  summarize(mean_weight = mean(wgt, na.rm = TRUE))
```














