---
title: "Text Processing"
author: "Shekhar Lamichhane Magar"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# List of String Manipulation Functions

```{r}
text <- "san francisco"
typeof(text)

num <- c("24","34","36")
typeof(num)
```

• Use sep feature to separate two characters
```{r}
var3 <- paste("Var1","Var2",sep="-")
var3
```
• Create 5 vectors and separate with ? and ! alternatively
```{r}
paste(1:5,c("?","!"),sep = "-")
paste
```

```{r}
text = "England"
cat (text, "USA", sep = "-")
```

```{r}
cat(month.name[1:5],sep=" ")
```

• Convert vectors to string
```{r}
toString(1:10)
```


• Load necessary library
```{r}
library(stringr)
str <- "Los Angeles, officially the city of Los Angeles and often known by its initials L.A., is the second-most popular city in the United States (after New York City), the most populous city in California and the county seat of Los Angeles County. Situated in Southern California, Los Angeles is knmown for its Mediterranean climate, ethnic diversity, sprawling metropolis, and as a major center of the American entertainment industry."
```

• Wrap text
```{r}
strwrap(str)
```

• Convert characters to lower and upper strings
```{r}
nchar(str)
str_length(str)

str_to_lower(str)

str_to_upper(str)
```


```{r}
# replace letter a,n,d get replaced by f,o,r
chartr("and", "for", x =str)

# For case sensitive strings
str_replace_all(string = str, pattern = c("City"), replacement = "state")
```


```{r}
substr(x=str, start = 5, stop = 11)

setdiff(c("monday", "tuesday", "wednesday"), c("monday", "thursday", "friday"))

setequal(c("monday", "tuesday", "wednesday"),c("monday", "tuesday", "wednesday"))
setequal(c("monday", "thursday", "friday"),c("monday", "thursday", "friday"))
```

• Abbreviate with a minimun length of 3
```{r}
abbreviate(c("monday","tuesday","wednesday"),minlength = 3)

#split string
strsplit(x = c("ID-101", "ID-102", "ID-103", "ID-104"),split = "-")

str_split(string = c("ID-101", "ID-102", "ID-103","ID-104"),pattern = "-", simplify = T)
```

Find and replace first match
```{r}

sub(pattern = "L", replacement = "B", x = str,ignore.case = T)

#find and replace all matches
gsub(pattern = "Los", replacement = "Bos", x = str,ignore.case = T)
```

## Meta characters


```{r}
dt <- c("20", "20$")
grep(pattern = "20\\$",x=dt, value = T)
```

```{r}
dt <- c("may?","money$", "and&")
gsub(pattern = "[\\?-\\$-\\&]", replacement = "", x =dt)
```

```{r}
gsub(pattern = "\\\\", replacement = "-", x = "Barcelona\\Spain")
```

```{r}
dt <- c("may?", "money$", "and$")
grep(pattern = "\\m", x = dt, value = T)
```

## Quantifiers

```{r}
names <- c("anna", "crissy", "puerto", "cristian", "garcia", "steven","alex", "rudy")

# doesn't matter if e is a match
grep(pattern = "e*",x=names,value = T)

#must match t one or more time
grep(pattern = "t+", x = names,value = T)

#must match n two times
grep(pattern = "n(2)",x=names, value = T)
```

## sequence

```{r}
str <- "I have been to Paris 20 times"

#match a digit
gsub(pattern = "\\d+", replacement = "_",x =str)
regmatches(str, regexpr(pattern = "\\d+", text = str))

# match a non digit
gsub(pattern = "\\D+", replacement = "_",x =str)
regmatches(str, regexpr(pattern = "\\D+", text = str))

#match a space - returns position
#grepexpr(pattern = "\\s+", text = str)

#match a non space
gsub(pattern = "\\S+", replacement = "app", x= str)

#match a word character
gsub(pattern = "\\w", replacement = "k", x = str)

# match a non word character
gsub(pattern = "\\W", replacement = "k",x=str)
```

# Character classes

```{r}
str <- "20 people got killed in a mob attack. 14 got severly injured"

#extract numbers
regmatches(x = str, gregexpr("[0-9]+", text = str))

# extract without digits
regmatches(x = str, gregexpr("[^0-9]+", text = str))
```
  
```{r}
str<- c("cat.", "896.", "?=+.", "abc1")
grepl(pattern = "...\\.", x =str)
```
  
```{r}
str <-c("aaaabc", "aabbbc", "aacc", "a")
grepl(pattern = "a+b*c", x =str)
```
```{r}
str <- c("warzzzzup", "wazzzup", "wazup")
grepl(pattern = "waz(3,4)up", x =str)
```

```{r}
str<- c("A. B", "c! d", "e f", "g. H3", "i> J", "k L")
grep(pattern = "[a-z]\\.?\\s+[A-Z]\\d*", x=str)
```

```{r}
str <- c("09/01/2016", "09/21/16", "12/25/2016", "12/06/16")
grep(pattern = "^([0-2][0-9]|(3)[0-1])(\\/)((0)[0-9}|(1)[0-2])(\\/)\\d(4)$", x=str)
```

```{r}
dt <- c("75 to 79", "80 to 84", "85 to 89")
```

```{r}
    first_values <- grep("^(75|80|85)", dt, value = TRUE)

first_values <- sub("^(\\d+).*", "\\1", first_values)

result <- toString(first_values)

result
```

