---
title: "Lab-2 Introduction to Data Science"
author: "Shekhar Lamichhane Magar"
date: "2024-06-13"
output: pdf_document
---


# Variables

task 1: Create variables x and y. Assign the prodct of x and y to z.
```{r}
x = 2+5
y = 6
z = x*y
z
```
task 2: Create variable a and b using arrow. Assign the value of a divided by b and finally print c.  
```{r}
a <- 10-7
b <- 4
c <- a/b
c
```
# Functions
Task 3: Create a function x using c() and store some value and print x.
```{r}
x = c(100,200,300)
x
```
# Data Types in R
task 3: Assign a value in x and use class() function to check its data type.
```{r}
x = 5
class(x)

```
task 4: Use is.integer() function to check if it is integer.
```{r}
is.integer(x)
```
# Vectors, Matrices, Arrays, Lists, and Data Frames
task 5: Create matrix xx and print it.
```{r}
xx = matrix(1:6, nrow=3, ncol=2)
xx
```
task 6: Use class() is.vector() is.matrix(), length(), dim() functions to check class length and number of rows and column.
```{r}
class(xx)
is.vector(xx)
is.matrix(xx)
length(xx)
dim(xx)
```
# Datasets for apply family tutotial
task 7: Load pre-built data named "mtcars" and use head() function to see some rows and columns of data.

```{r}
data("mtcars")
head(mtcars)
```
task 8: Use apply function to apply max row wise.

```{r}
apply (t(beaver1),1,max)
```
task 9: Use apply function in mtcars dataset to find mean column wise by passing 2 in second parameter.
```{r}
apply(mtcars, 2, mean)
```
task 10: Use apply() function in head of matcars dataset column wise and apply function x which gives reminder.
```{r}
head(apply(mtcars, 2, function(x) x%%10))
```
# lapply() function

task 11: Make variable named movies and use lapply() function and pass tolower parameter to movise variable.
```{r}
movies <- c("SPYDERMAN","BATMAN","VERTIGO","CHINATOWN")
movies_lower <- lapply(movies, tolower)
str(movies_lower)
```
task 12: Use unlist() function to convert the list into a vector.
```{r}
movies_lower <- unlist(lapply(movies, tolower))
str(movies_lower)
```
# sapply() function

task 13: Use sapply() function that takes list, vector or data frame as input and gives output in vector or matrix.
```{r}
dt <- cars
lmn_cars <- lapply(dt, min)
smn_cars <- sapply(dt, min)
lmn_cars
```
```{r}
lmxcars <- lapply(dt, max)
smcars <- sapply(dt, max)
lmxcars
```
task 14: Create a function avg and pass this function in sapply to get the result.
```{r}
avg <- function(x) {
  (min(x) + max(x)) / 2}
fcars <- sapply(dt, avg)
fcars
```
# Saving and Loading Data
task 15: Create two vectors and convert it into data frame.
```{r}
EUCountryNames = c("United Kingdom", "Germany","France","Italy")
EUPopulation = c(324542,243234524,2345452,234522345)
EU = data.frame(EUCountryNames, EUPopulation)
EU
```
```{r}
save(EU, file = "EUInfo.RData")
```
task 16: Use getwd() function
```{r}
getwd()
```
task 17: Load the data
```{r}
rm(EU)
load("EUInfo.RData")
EU
```
task 18: Convert the data into csv file
```{r}
write.csv(EU,"EUInfo.csv")
```

task 19: load the csv file
```{r}
EU2 = read.csv("EUInfo.csv")
EU2
```
task 20: install xlsx
```{r}
library(xlsx)

```
task 21: convert into xlsx format
```{r}
write.xlsx(EU, "EUInfoNew.xlsx", sheetName="Sheet1")
```
task 22: load the file 
```{r}
EU3 = read.xlsx("EUInfoNew.xlsx", sheetName="Sheet1")
EU3
```














