---
title: "Data Manipulation_Lab-7(Part 1)"
author: "Shekhar Lamichhane Magar"
output:
  pdf_document: default
  html_notebook: default
---

## Lab: Data Manipulation

Task: Load and Read yrbss_demo.csv file
```{r}
# import libraries
library(tidyverse)

demo_data <- read_csv("yrbss_demo.csv")
```

# 1) Filter Rows
### a) Filter by position
Task: first 6 rows of demo_data.
```{r}
# Brackets method 
slice(demo_data, 1:6)

# Pipe method
demo_data %>% slice(1:6)
```

### Filter by logical criteria

Task: Filter rows with age less than 15
```{r}
# Bracket method
demo_data[demo_data$age<15,]

# Pipe method
demo_data %>% filter(age<15)
```

Task: Filter rows using equality
```{r}
demo_data %>% filter(sex == "Female")
demo_data %>% filter(!(grade == "9th"))
```

Task: Filter rows using OR operator
```{r}
demo_data %>% filter((bmi < 15) | (bmi > 50))
```

Task: Filter rows using %in% operator

```{r}
demo_data %>% filter(grade %in%  c("10th", "11th"))
```

Task: Filter rows by multiple-column based criteria
```{r}
demo_data %>% filter(bmi < 20, stweight < 50, sex == "Male")
```

Q1 : Write the code to filter rows with percentage of bmi/stewight <0.5
```{r}
demo_data %>% filter((bmi/stweight) < 0.5)
```

### c ) Filter within a selection of variables
Task: Create temporary data set named "temp_data" using bmi and stweight
```{r}
temp_data <- demo_data %>% select(bmi, stweight)
```

Task: Filter rows in temp_data where all variables are grater than 2.4
```{r}
temp_data %>% filter_all(all_vars(.>2.4))
```

Task: Filter rows in temp_data where any of the variable are greater than 2.4
```{r}
temp_data  %>% filter_all(any_vars(.>2.4))
```

Task: Filter rows in demo_data where race values are "White."
```{r}
demo_data %>% filter_at(vars(starts_with("race")), any_vars(.=="White"))
```

Task: Filter rows 
```{r}
demo_data %>% filter_at(vars(starts_with("race")), any_vars(.=="Asian"))
```

Task: Filter rows in demo_data which have none NA values for all numeric variables
```{r}
demo_data %>% filter_if(is.numeric, all_vars(!is.na(.)))
```

### d) Select random rows from a data frame 

```{r}
set.seed(1234)
# Extract 5 random rows without replacement 
demo_data %>% sample_n(5, replace = FALSE)

# Extract 5% of rows, randomly without replacement 
demo_data %>% sample_frac(0.05, replace = FALSE)
```

### e) Select top n rows ordered by a variable
Task: Select the top 5 rows ordered by bmi
```{r}
demo_data %>% top_n(5, bmi)
```

Task: Select the top 5 rows ordered by bmi in all
```{r}
demo_data %>% group_by(grade) %>% top_n(5, bmi)
```

# 2) Column operations
### a) Select columns
Task: Select columns record, age and sex (or columns from record too sex)

```{r}
# Brackets
demo_data[, c("record","age","sex")]
# Pipes
demo_data %>% select(record, age, sex)
demo_data %>% select(record:sex)
```

## Practice exercise
Q. What is the meaning of each?
In the first line of code, the columns from 'record' to 'sex' are selected from 'demo_data', and in the second line, 'age' and 'stweight' are selected. The main difference is that even if there is no column with the given name inside 'one_of', it will simply select the ones that are present.

```{r}
# What is the meaning of each?
demo_data %>% select(record:sex)
demo_data %>% select(one_of(c("age","stweight")))
```

```{r}
# Select all columns except 'age' and 'sex'
demo_data %>% select(-age, -sex)
```

```{r}
# Select all columns except from 'record' to 'sex'
demo_data %>% select(-(record:sex))
```

```{r}
# Select columns that contain "race"
demo_data %>% select(contains("race"))
```

```{r}
# Select columns that start with "r"
demo_data %>% select(starts_with("r"))
```


Q2: Explain the meaning of the output of: demo_data %>% select(-contains("r"))?
ANS: It selects the columns excluding all other containing r

## b) Rename column
```{r}
#renames column variables
demo_data %>% rename(id = record)
```



## c) Add a new column

```{r}
demo_data %>% mutate(height_m = sqrt(stweight / bmi))
```



Q3: Check the data frame. Has the new column added? re-write the above command in a way
to add the column if not.
ANS: Yes, the column is added.






