---
title: "Exploratory data analysis_Lab10(part1)"
author: "Shekhar Lamichhane Magar"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

Task: Load the csv file
```{r}
MS_country_stops <- read.csv("MS_county_stops.csv")
MS_traffic_stops <- read.csv("MS_trafficstops_bw_age.csv")
```

## 1) Get data summaries
Task: Getting data summaries
```{r}
str(MS_country_stops)
```

```{r}
summary(MS_country_stops)
```


## 2) Plotting with ggplot2
Task: Importing the necessary library for this project
```{r}
# Importing the library
library("tidyverse")
```

Task: Using ggplot scatterplot male and female

```{r}
ggplot(data = MS_country_stops, aes(x = male, y = female)) + geom_point()
```

Task: Using pipeline operator

```{r}
MS_country_stops %>% ggplot(aes(x = male, y = female)) + geom_point()
```

Task: Storing the function in variable and using the same variable to create two plots
```{r}
# Assign plot to a variable
MS_plot <- ggplot(data = MS_country_stops, aes(x = male, y = female))

# Draw the plot with data points
MS_plot + geom_point()

# Draw the plot using lines
MS_plot + geom_line()
```

### a) Scatter plot
Task: using ggplot for plotting male and female in scatter plot 
```{r}
MS_country_stops %>% ggplot(aes(x = male, y = female)) + geom_point()
```

Task: Using alpha and color for different visuals
```{r}
MS_country_stops %>% ggplot(aes(x = male, y = female)) + geom_point(alpha = 0.3, color = "blue")
```

Task: Adding line to show linear realation
```{r}
MS_country_stops %>% ggplot(aes(x = male, y = female)) + geom_point(alpha = 0.3, color = "blue") + geom_abline()
```

### b) Boxplot
Task: using boxplot to plot violation clolumn of driver_age dataset
```{r}
boxplot(driver_age~violation, data = MS_traffic_stops)
```

```{r}
boxplot(driver_age~violation, data = MS_traffic_stops, las = 2)
```

Task: Let’s see how to draw boxplots using the ggplot function.
```{r}
MS_traffic_stops %>% ggplot(aes(x = violation, y = driver_age)) + geom_boxplot()
```

Task: Filtering missing value and drawing boxplot
```{r}
# Filter missing values of driver_age
filtered_MS_traffic_stops <- MS_traffic_stops %>% filter(!is.na(driver_age)) 

# Draw boxplot
ggplot(filtered_MS_traffic_stops, aes(x = violation, y = driver_age)) + geom_boxplot()
```

Task: Storing data in variable 
```{r}
Yazoo_stops <- MS_traffic_stops %>% filter(county_name == "Yazoo County", !is.na(driver_age))
```

Task: overlapping two plots box plot and point plot
```{r}
Yazoo_stops %>% ggplot(aes(x = violation, y = driver_age)) + geom_boxplot() + geom_point()
```

Task: overlapping two plots box plot and jitter to avoid the contraction of points in single line
```{r}
Yazoo_stops %>% ggplot(aes(x = violation, y = driver_age)) + geom_boxplot() + geom_jitter()
```

Task: using color and alpha
```{r}
Yazoo_stops %>% ggplot(aes(x = violation, y = driver_age)) + geom_boxplot() + geom_jitter(alpha = 0.5, color = "tomato")
```

Task: overlapping boxplot over the point
```{r}
Yazoo_stops %>% ggplot(aes(x = violation, y = driver_age)) + geom_jitter(alpha = 0.5, color = "tomato") + geom_boxplot()
```

Task:  using alpha to see both 
```{r}
Yazoo_stops %>% ggplot(aes(x = violation, y = driver_age)) + geom_jitter(alpha = 0.5, color = "tomato") + geom_boxplot(alpha = 0)
```


### c) Histograms
Task: plotting in histogram
```{r}
MS_traffic_stops$driver_age %>% hist(col="gold")
```

Task: using col and fill to make different visual
```{r}
MS_traffic_stops %>% ggplot(aes(driver_age)) + geom_histogram(col = "red", fill = "green", alpha = 0.2)
```
Task: Defining  count and using break sequence with lower and upper bound and bin range in histogram.

```{r}
# Define bin count 
ggplot(MS_traffic_stops, aes(driver_age)) + geom_histogram(col = "red", fill = "green", alpha=0.2, bins = 20)

# Use break sequence with lower bound, upper bound and bin range
ggplot(MS_traffic_stops, aes(driver_age)) + geom_histogram(col = "red", fill = "green", alpha = 0.2, breaks = seq(10, 50, by=2))
```

Task: Adding title and coustomiaing x and y label
```{r}
ggplot(MS_traffic_stops, aes(driver_age)) + geom_histogram(col="red", 
fill="green", alpha=0.2, breaks=seq(10, 50, by=2)) + labs(title="Histogram for 
Age", x="Age", y="Count")
```

Task: using gradient
```{r}
ggplot(MS_traffic_stops, aes(driver_age)) + geom_histogram(alpha=0.2, 
breaks=seq(10, 50, by=2), col="red", aes(fill=..count..)) +
scale_fill_gradient("Count", low="green", high="red")
```


### d) Bar charts/ Bar plots
Task: Displaying frequency of each category and drawing bar chart
```{r}
# Display the frequency of each category
table(MS_traffic_stops$violation)

# Draw bar chart
barplot(table(MS_traffic_stops$violation),col = "red", main="Number of
violations")

```

Task: Using barplot
```{r}
ggplot(MS_traffic_stops, aes(violation)) + geom_bar()
```

Task: using fill
```{r}
ggplot(MS_traffic_stops, aes(violation)) + geom_bar(fill = "green")
```

Q2: What will happen if you use “col” instead of “fill”?
Ans: The border of the bar will be green.


Task: using fill in aes to see male and female in same plot 
```{r}
MS_traffic_stops %>% ggplot(aes(violation)) + geom_bar(aes(fill = driver_gender))
```

Task: using fill in aes to see male and female in same plot 
```{r}
MS_traffic_stops %>% ggplot(aes(violation)) + geom_bar(aes(fill = driver_gender), position = "fill")
```

Task: using fill in aes to see male and female in same plot in vertical
```{r}
MS_traffic_stops %>% ggplot(aes(violation)) + geom_bar(aes(fill = driver_gender), position = "fill") + coord_flip()
```

Q3: From your graphs, do you think male are likely to break lights than
females? How about speeding?
Ans:  Yes, I think male are likely to break lights than females and also for speeding.


## 3) Correlation Analysis

```{r}
movies <- read.csv("movies.csv")
```

### a) Graphical Analysis
 
```{r}
movies %>% ggplot( aes(x=revenue, y=budget)) + geom_point(alpha = 0.3, color = "blue") + geom_abline()
```

### b) Quantitative Analysis
Task: Getting quantative analysis
```{r}
cor(movies$vote_average, movies$revenue)
```

### c) Correlation Matrix 
Task: correlation plot
```{r}
# Install.packages("GGally")
# Load package
library(GGally)
# Generate correlation matrix
ggcorr(movies)
```

Q4: what is the correlation between vote_count and runtime?
Ans: There is positive correlation between vote_count and runtime.

Task: correlation plot and also value
```{r}
ggcorr(movies, label=TRUE, label_alpha = 0.3)
```

Task: Creating scatter plot more relation.

```{r}
ggplot(data = movies, aes(x = revenue, y = vote_count)) + geom_point(alpha=0.3, color = "blue")
```

Task: Adding trend line to make it even clear relation between variables.
```{r}
qplot(movies$revenue, movies$vote_count, data=movies , geom= c("point",
"smooth" ), method= "lm", alpha= I (1/5), se= FALSE)

```

Q5: What is the correlation type shown in the resulted plot?
Ans: The correlation type shown in the resulting plot is a linear correlation.

