---
title: "R Lab_2_notebook"
author: "Shekhar Lamichhane Magar"
output: html_notebook
---

# variables

task 1: Create variable x and y. Store the product of both variable into z
and print the value.

```{r}
x<-2+5
y<-6
z<-x*y
z
```
task 2: create variable a, b and c. assign subtraction product in variable
'a' and store product into b and divide the variable a and b and store the
value into c.
```{r}
a<-10-7
b<-4
c<-a/b
c
```
# Functions

Task 1: Create one variable x and assign the c() function into  and give
these values(100, 200, 300) into function and print the variable x.

```{r}
x<-c(100, 200, 300)
x

```

Task 2: Use ? or help() function to understand the particular function.


```{r}
help(c)
```



# DataTypes in R

Task 1: create variable x and give the value 5 into x and use the class
function to check the data type of a variable.

```{r}
x<-5
class(x)
```
Task 2: Use another class function to check the variable stores value as a
integer or not.

```{r}
is.integer(x)
```

# Vectors, Matrices, Arrays, Lists, and Data Frames.

Task 1: Create a matrix named 'xx' and use the 'matrix()' function and give
several arguments and values to popi=ulate the matrix from the sequence of 
integers from 1 to 6. specify the columns and rows in a matrix to 2 and 3.

```{r}
xx<-matrix(1:6, nrow<-3, ncol<-2)
xx
```
Task 2: Specify the class of matrix.

```{r}
class(xx)
```
Task 3: Specify the value is vector or not.

```{r}
is.vector(xx)
```
Task 4: Specify the value is matrix or not.

```{r}
is.matrix(xx)
```
Task 5: To specify the length.

```{r}
length(xx)
```
Task 6: To understand the dimension(dm) that is row and column.

```{r}
dim(xx)
```

# Datasets for apply functions

Task 1: Load the dataset "mtcars" and display the first few rows of the dataset.

```{r}
data("mtcars")
head(mtcars)
```

# apply() function:

## data matrix
## row/column operation, – 1 for row wise operation, 2 for column wise operation
## function to be applied on the data.

Task 1: There are 3 arguments and when 'Margin=1' is passed as the second
parameter and the function max is applied row wise and gives the result.

```{r}
apply(t(beaver1),1,max)

```
Task 2: when 'Margin=2' is passed as the second parameters and the function 
mean is applied column wise.


```{r}
apply(mtcars,2,mean)
```
Task 3: Passing Custom function instead of default functions and applying the
modulus operation.

```{r}
head(apply(mtcars,2,function(x) x%%10))
```

# lapply() funtion:

Task 1: Creating a vector of movie titles and using 'lappply()' to convert to 
lowercase and again checking the structure of the result.

```{r}
movies <- c("SPYDERMAN","BATMAN","VERTIGO","CHINATOWN")
movies_lower <-lapply(movies, tolower)
str(movies_lower)

```
Task 2: using unlist() to convert the list into a vector.

```{r}
movies_lower <-unlist(lapply(movies,tolower))
str(movies_lower)
```
# sapply() function:

Task 1: Measure the minimum speed and stopping distances of cars from the cars
dataset using lapply and sapply.

# sapply function returns a vector.

```{r}
dt <- cars
lmn_cars <- lapply(dt, min)
smn_cars <- sapply(dt, min)
lmn_cars
smn_cars
```
```{r}
lmxcars <- lapply(dt, max)
smxcars <- sapply(dt, max)
lmxcars
```
Task 2: Create custom function named 'avg' that is the average of the minimum 
and maximum values of a vector then use 'sapply', 'avg()', and 'dt'=dataset.

```{r}
avg <- function(x) {
  (min(x) + max(x)) / 2
}

fcars <- sapply(dt, avg)
fcars
```

# Saving and Loading Data

The native data format in R is called RData. For example, let’s use the data
frame for European countries to store the data on disk.

Task 1: Create a data frame named 'EU' and add some information about 
European countries' names and population.

```{r}
EUCountryNames <- c("United Kingdom", "Germany","France","Italy")
EUPopulation <- c(63843856, 82562004,64982894,61142221)
EU <- data.frame(EUCountryNames,EUPopulation)
EU
```
Task 2: Storing the data on disk in the native R format RData.

```{r}
save(EU, file<-"EUInfo.RData")
```
Task 3: If we want to see the created file in our working directory 
then use getwd() function.

```{r}
getwd()
```

Task 4: Our Data should be stored in CSV or excel sheets.
To add or save file in csv and excel then use 
'write.csv()' and 'write.xlsx()'

```{r}
write.csv(EU,"EUinfo.csv")
```

Task 5: To read the file's context from the disk.

```{r}
EU1 <- read.csv("EUInfo.csv")
EU1
```

Task 6: To save data to an excel file should install the package first.

```{r}
install.packages("xlsx")
install.packages("readxl")
library(xlsx)
library(readxl)

## Loading required package: rJava
## Loading required package: xlsxjars
```

Task 7: Now, Store and load the data in 
Excel format. Use the 'write.xsls(); 
function to save the data frame to an Excel file.

* eg.  Suppose we have a data frame named 'my.data' and it will save the
data frame 'my.data' to an Excel file named 'EUInfoNew.xlsx'.

```{r}
write.xlsx(EU,"EUInfoNew.xlsx",sheetName="Sheet1")
```

Task 8: Use the 'read.excel()' function to read 
the Excel file.
```{r}
EU3 <- read.xlsx("EUInfoNew.xlsx",sheetName="Sheet1")
EU3
```

